Hydrodynamics of a Semi-Permeable Vesicle Under Flow and Confinement???

### 2020-12-16 vesicle_code/docs/permeableVes/main.tex
working on figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry}

Velocity scale is $100\mu$m/s.

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
  the vesicle height is initially $10\mu$m, and the maximum background
  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
  into the vesicle, and the fluid flux along the blue regions is out of
  the vesicle.}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
We expose a single semi-permeable vesicle to even larger deformations by
simulating its hydrodynamics in a contracting microfluidic geometry.
Similar to~\cite{wu2015critical}, we consider a geometry whose width
gradually reduces from $16\mu$m to $1.6\mu$m and then immediately opens
again to $16\mu$m. We initialize a semi-permeable vesicle with $\alpha =
0.65$ that spans $10\mu$m of the total channel width. We start by
investigating whether the vesicle passes through the constriction with
different flow rates and permeability rates.

\begin{figure*}[htp]
  \centering
%  \ifTikz
  \input{figures/contractingComposite.tikz}
%  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
  the vesicle height is initially $10\mu$m, and the maximum background
  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
  into the vesicle, and the fluid flux along the blue regions is out of
  the vesicle.}
\end{figure*}
